---
title: "mastercap_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mastercap_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mastercap)
require(magrittr)
```

# Mastercap Earthquake Data Visualization Package

The goal of this package ('mastercap') is to provide a few simple tools to make it easier to visualize earthquake data. It is part of the final capstone of the Mastering Software Development in R Coursera specialization.

The four main functions are:
1. clean_eq_data() takes raw earthquake data and reformats it into a tidy Tibble
2. geom_timeline() takes an earthquake Tibble and produces a visual timeline of earthquakes
3. geom_timeline_label() is the same as geom_timeline() but also adds labels
4. eq_map() plots earthquakes on an interactive, annotated map

## Example

The first example cleans the raw data and produces an earthquake timeline to display earthquakes in China, Russia, and Japan between Jan 1, 2008, and Jan 1, 2010.

```{r}
library(mastercap)
data("raw_data.rda")
raw_data %>%
  clean_eq_data() %>%
  geom_timeline(mindate = "2008-01-01",
                maxdate = "2010-01-01",
                countries = c("China", "Russia", "Japan"))
```

The second example demonstrates the same plot but uses the geom_timeline_label function.

```{r}
library(mastercap)
data("raw_data.rda")
raw_data %>%
  clean_eq_data() %>%
  geom_timeline_label(mindate = "2008-01-01",
                      maxdate = "2010-01-01",
                      countries = c("China", "Russia", "Japan"))
```

The final example demonstrates eq_map. It uses the same filtered data.

```{r}
library(mastercap)
data("raw_data.rda")
raw_data %>%
  clean_eq_data() %>%
  dplyr::filter(date >= "2008-01-01",
         date <= "2010-01-01",
         country == c("China", "Russia", "Japan")) %>%
  eq_map()
```
